---
title: "p8105_hw1_ts3670"
author: "Tong Su"
date: "2024-09-20"
output:
  pdf_document: default
---
```{r}
library(tidyverse)
library(ggplot2)
```

# Problem 1
# Load the penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
```
# Short Discription

The `penguins` shows 8 variables about the information of penguins including `species`, `island`, `bill_length_mm`, `bill_depth_mm`, `flipper_length_mm`, `body_mass_g`, `sex`, `year`. It has `r nrow(penguins)` rows and `r ncol(penguins)` columns. The mean of `flipper_length_mm` is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`.

# Scatterpolot and Saving 
```{r}
plot_df = ggplot(penguins,  aes(x = bill_length_mm, y = flipper_length_mm, colour =species )) + geom_point(na.rm = TRUE) + labs(title = "Bill_length_mm vs Flipper_length_mm")
```
```{r}
ggsave("Bill_length_mm vs Flipper_length_mm.jpg", plot = plot_df)
```
# Problem 2
#Data Frame
```{r}
set.seed(123)

random_sample = rnorm(10, mean = 0, sd = 1)
logical_vector = random_sample > 0
character_vector = c('Empathy', 'Self-awareness', 'Adaptability',
'Curiosity', 'Motivation', 'Analytics', 'Passionate', 'Optimism', 'Open-Minded',  'Belief')
factor_vector = factor(sample(c('low', 'medium', 'high'), size = 10, replace = TRUE))

df = data.frame(random_sample, logical_vector, character_vector, factor_vector)

df
```
#Mean of each variable in the data frame
```{r}
mean_random_sample = mean(df %>% pull(random_sample))
mean_logical_vector = mean(df %>% pull(logical_vector))
mean_character_vector = try(mean(df %>% pull(character_vector)), silent=FALSE) 
mean_factor_vector = try(mean(df %>% pull(factor_vector)), silent=FALSE)
# results
print(mean_random_sample)
print(mean_logical_vector)
print(mean_character_vector)
print(mean_factor_vector)
```
Illustration: `character_vector` and `factor_vector` are not numerical nor logical so they cannot be taken the mean.

#Convert variables to numeric
```{r}
numeric_logical = as.numeric(logical_vector)
numeric_character = (as.numeric(character_vector))
numeric_factor = (as.numeric(factor_vector))

# output the result
print(numeric_logical)
print(numeric_character)
print(numeric_factor)
```


